### 2016-06-27 Manuscript/SW_early_life_telomeres.Rmd
More edits

###Results
We measured telomere lengths using a total of `r nrow(dd)` unique samples from juvenile and adult Seychelles warblers. Of these, `r length(unique(subset(dd,Agemonths<12)$BirdID))` samples were taken cross-sectionally from birds caught within their first year of life. Efficiencies (mean $\pm$ s.d.) for our telomere and GAPDH reactions were (`r round2(mean(dd$EffTelomere))` $\pm$ `r round2(sd(dd$EffTelomere))`) and (`r round2(mean(dd$EffGAPDH))` $\pm$ `r round2(sd(dd$EffGAPDH))`) respectively. Inter-plate repeatability of RTL, based on `r nrow(subset(ddL,Group == 'Within samples'))` samples measured at least twice, was 0.78 (CI = 0.73-0.82).

#####Early-life RTL
Using the cross-sectional data RTL decreased with age across the entire lifespan of the Seychelles warbler (LMM: t = `r round2(summary(lme(RTL~Agemonths,data=dd,random=~1|BirdID))$tTable[2,4])`; P `r round3(summary(lme(RTL~Agemonths,data=dd,random=~1|BirdID))$tTable[2,5])`), although there were clear increases in (cross-sectional) telomere length after one year of age and at several points later in life (Fig. 1A). RTL also decreased with age within the first year of life (i.e. excluding adult samples; t = `r round2(summary(lme(RTL~Agemonths,data=juv,random=~1|BirdID))$tTable[2,4])`; P `r round3(summary(lme(RTL~Agemonths,data=juv,random=~1|BirdID))$tTable[2,5])`). In the longitudinal analysis RTL decreased with age within individuals (i.e. with $\Delta$age; t = `r round2(summary(lme(RTL~DeltaAge,data=subset(dd,DeltaAge!=0),random=~1|BirdID))$tTable[2,4])`; P = `r round3(summary(lme(RTL~DeltaAge,data=subset(dd,DeltaAge!=0),random=~1|BirdID))$tTable[2,5])`; Fig. 1B).

Early-life RTL varied significantly among cohorts (Likelihood ratio test: F = `r round2(anova(lme(RTL~factor(FieldPeriodID),data=juv,random=~1|BirdID))[2,3])`; P `r round3(anova(lme(RTL~Agemonths,data=juv,random=~1|BirdID))[2,4])`). Cohort-level variation in juvenile RTL was not related to adult population density (LMM controlling for age and cohort: t = `r round2(summary(lme(RTL~Agemonths+Density,data=juv,random=~1|FieldPeriodID))$tTable[3,4])`; P = `r round3(summary(lme(RTL~Agemonths+Density,data=juv,random=~1|FieldPeriodID))$tTable[3,5])`), or to temporal variation in  food availability (t = `r round2(summary(lme(RTL~Agemonths+Insect,data=juv,random=~1|FieldPeriodID,na.action=na.exclude))$tTable[3,4])`; P = `r round3(summary(lme(RTL~Agemonths+Insect,data=juv,random=~1|FieldPeriodID,na.action=na.exclude))$tTable[3,5])`).

@@

#####Early-life telomere shortening
Longitudinal data showed that early-life RTL was not related to adult RTL (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=Loss))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=Loss))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = Loss))$coefficients[2,4])`; Fig. 4A). Running this analysis separately for juvenile age classes revealed that this relationship was not significant for nestlings (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 1)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 1)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(Loss,Agemonths == 1)))$coefficients[2,4])`), fledglings (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 6)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 6)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(Loss,Agemonths == 6)))$coefficients[2,4])`) or subadults (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 10)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 10)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(Loss,Agemonths == 10)))$coefficients[2,4])`). $\Delta$RTL was significantly lower than zero in nestlings (t = `r round2(t.test(subset(Loss,Agemonths == 1)$Loss)$statistic)`; P `r round3(t.test(subset(Loss,Agemonths == 1)$Loss)$p.value)`), but not in fledglings (t = `r round2(t.test(subset(Loss,Agemonths == 6)$Loss)$statistic)`; P = `r round2(t.test(subset(Loss,Agemonths == 6)$Loss)$p.value)`) or subadults (t = `r round2(t.test(subset(Loss,Agemonths == 10)$Loss)$statistic)`; P = `r round2(t.test(subset(Loss,Agemonths == 10)$Loss)$p.value)`), suggesting that telomere shortening was highest shortly after the nestling phase, after which both telomere shortening and telomere lengthening were observed (Fig. 4B).

#####Early-life telomere dynamics and survival

Early-life RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~cenTL+Agemonths+(1|PlateID)+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~cenTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,4])`), with no interaction effect between RTL and juvenile age (estimate = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[4,4])`), suggesting that there were no age-specific effects of juvenile RTL on survival to adulthood. To test whether cohort-level effects on RTL influenced survival we calculated cohort-level RTL (i.e. the median RTL for each cohort) and added this term to a GLMM, and found that cohort-level RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv13,family = 'binomial'))$coefficients[2,4])`). Using the longitudinal data, we found that $\Delta$RTL had no effect on survival to the year after the second sampling event (estimate = `r round2(summary(glm(SurvivedNext2~Loss+Agemonths,data = subset(Loss,LayYear<2013),family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext2~Loss+Agemonths,data=subset(Loss,LayYear<2013),family = 'binomial'))$coefficients[2,4])`).

Cox regression showed no effect of individual-level or cohort-level RTL on survival later in life (individual-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL+Agemonths+frailty(FieldPeriodID))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL+Agemonths+frailty(FieldPeriodID))))$coefficients[1,6])`; cohort-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL*Agemonths+RTL+frailty(FieldPeriodID))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL*Agemonths+RTL+frailty(FieldPeriodID))))$coefficients[1,6])`), and no interaction between RTL and juvenile age on survival (individual-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,6])`; cohort-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,6])`). $\Delta$RTL was not related to longer-term survival (estimate `r round3(summary(coxph(with(subset(Loss,LayYear<2008),Surv(RemainingLife2+1,Died)~Loss+Agemonths)))$coefficients[1,1])`, P = `r round2(summary(coxph(with(subset(Loss,LayYear<2008),Surv(RemainingLife2+1,Died)~Loss)))$coefficients[1,5])`).

@@

>>>>

###Results
We measured telomere lengths using a total of `r nrow(dd)` unique samples from juvenile and adult Seychelles warblers. Efficiencies (mean $\pm$ s.d.) for our telomere and GAPDH reactions were (`r round2(mean(dd$EffTelomere))` $\pm$ `r round2(sd(dd$EffTelomere))`) and (`r round2(mean(dd$EffGAPDH))` $\pm$ `r round2(sd(dd$EffGAPDH))`) respectively. Inter-plate repeatability of RTL, based on `r nrow(subset(ddL,Group == 'Within samples'))` samples measured at least twice, was 0.78 (CI = 0.73-0.82).

#####Telomere dynamics and age
Using the cross-sectional data RTL decreased with age across the entire lifespan of the Seychelles warbler (LMM: t = `r round2(summary(lme(RTL~Agemonths,data=dd,random=~1|BirdID))$tTable[2,4])`; P `r round3(summary(lme(RTL~Agemonths,data=dd,random=~1|BirdID))$tTable[2,5])`). We found that modelling a non-linear effect age explained almost double the variation in telomere length (R^2^ of linear regression of telomere length and log age = `r round3(summary(lm(RTL~log(Agemonths),data=dd))$r.squared)` than a linear model `r round3(summary(lm(RTL~Agemonths,data=dd))$r.squared)`. Also worth noting is that while the overall trend was for decreasing delomre length, there were clear increases in cross-sectional telomere length after one year of age and at several points later in life (Fig. 1A). RTL also decreased with age within the first year of life (i.e. excluding adult samples; t = `r round2(summary(lme(RTL~Agemonths,data=juv,random=~1|BirdID))$tTable[2,4])`; P `r round3(summary(lme(RTL~Agemonths,data=juv,random=~1|BirdID))$tTable[2,5])`). In the longitudinal analysis RTL decreased with age within individuals (i.e. with $\Delta$age; t = `r round2(summary(lme(RTL~DeltaAge,data=subset(dd,DeltaAge!=0),random=~1|BirdID))$tTable[2,4])`; P = `r round3(summary(lme(RTL~DeltaAge,data=subset(dd,DeltaAge!=0),random=~1|BirdID))$tTable[2,5])`; Fig. 1B).

Longitudinal data showed that early-life RTL was not related to adult RTL (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=Loss))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=Loss))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = Loss))$coefficients[2,4])`; Fig. 4A). Running this analysis separately for juvenile age classes revealed that this relationship was not significant for nestlings (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 1)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 1)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(Loss,Agemonths == 1)))$coefficients[2,4])`), fledglings (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 6)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 6)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(Loss,Agemonths == 6)))$coefficients[2,4])`) or subadults (R^2^ = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 10)))$r.squared)`; t = `r round2(summary(lm(RTL1~RTL+Agemonths,data=subset(Loss,Agemonths == 10)))$coefficients[2,3])`; P = `r round2(summary(lm(RTL1~RTL+Agemonths,data = subset(Loss,Agemonths == 10)))$coefficients[2,4])`). $\Delta$RTL was significantly lower than zero in nestlings (t = `r round2(t.test(subset(Loss,Agemonths == 1)$Loss)$statistic)`; P `r round3(t.test(subset(Loss,Agemonths == 1)$Loss)$p.value)`), but not in fledglings (t = `r round2(t.test(subset(Loss,Agemonths == 6)$Loss)$statistic)`; P = `r round2(t.test(subset(Loss,Agemonths == 6)$Loss)$p.value)`) or subadults (t = `r round2(t.test(subset(Loss,Agemonths == 10)$Loss)$statistic)`; P = `r round2(t.test(subset(Loss,Agemonths == 10)$Loss)$p.value)`), suggesting that telomere shortening was highest shortly after the nestling phase, after which both telomere shortening and telomere lengthening were observed (Fig. 4B).

#####Early life environment and telomere dynamics
Early-life RTL varied significantly among cohorts (Likelihood ratio test: F = `r round2(anova(lme(RTL~factor(FieldPeriodID),data=juv,random=~1|BirdID))[2,3])`; P `r round3(anova(lme(RTL~Agemonths,data=juv,random=~1|BirdID))[2,4])`). Cohort-level variation in juvenile RTL was not related to adult population density (LMM controlling for age and cohort: t = `r round2(summary(lme(RTL~Agemonths+Density,data=juv,random=~1|FieldPeriodID))$tTable[3,4])`; P = `r round3(summary(lme(RTL~Agemonths+Density,data=juv,random=~1|FieldPeriodID))$tTable[3,5])`), or to temporal variation in  food availability (t = `r round2(summary(lme(RTL~Agemonths+Insect,data=juv,random=~1|FieldPeriodID,na.action=na.exclude))$tTable[3,4])`; P = `r round3(summary(lme(RTL~Agemonths+Insect,data=juv,random=~1|FieldPeriodID,na.action=na.exclude))$tTable[3,5])`).

@@

#####Early-life telomere dynamics and survival
Early-life RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~cenTL+Agemonths+(1|PlateID)+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~cenTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[2,4])`), with no interaction effect between RTL and juvenile age (estimate = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glmer(SurvivedNext~RTL*Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[4,4])`), suggesting that there were no age-specific effects of juvenile RTL on survival to adulthood. To test whether cohort-level effects on RTL influenced survival we calculated cohort-level RTL (i.e. the median RTL for each cohort) and added this term to a GLMM, and found that cohort-level RTL was not related to survival to adulthood (estimate = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glmer(SurvivedNext~cohortTL+RTL+Agemonths+(1|TerritoryID)+(1|FieldPeriodID),data=juv14,family = 'binomial'))$coefficients[2,4])`). Using the longitudinal data, we found that $\Delta$RTL had no effect on survival to the year after the second sampling event (estimate = `r round2(summary(glm(SurvivedNext2~Loss+Agemonths,data = subset(Loss,LayYear<2013),family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext2~Loss+Agemonths,data=subset(Loss,LayYear<2013),family = 'binomial'))$coefficients[2,4])`).

summary(glmer(SurvivedNext~RTL+(1|BirdID),data=subset(dd,LayYear<2000), family = 'binomial'))

Cox regression showed no effect of individual-level or cohort-level RTL on survival later in life (individual-level: estimate = `r round2(summary(coxph(with(juv12,Surv(Lifespan,Died)~RTL+Agemonths+frailty(FieldPeriodID))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv12,Surv(Lifespan,Died)~RTL+Agemonths+frailty(FieldPeriodID))))$coefficients[1,6])`; cohort-level: estimate = `r round2(summary(coxph(with(juv12,Surv(Lifespan,Died)~cohortTL*Agemonths+RTL+frailty(FieldPeriodID))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv12,Surv(Lifespan,Died)~cohortTL*Agemonths+RTL+frailty(FieldPeriodID))))$coefficients[1,6])`), and no interaction between RTL and juvenile age on survival (individual-level: estimate = `r round2(summary(coxph(with(juv12,Surv(Lifespan,Died)~RTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,1])`, P = `r round2(summary(coxph(with(juv12,Surv(Lifespan,Died)~RTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,6])`; cohort-level: estimate = `r round2(summary(coxph(with(juv12,Surv(Lifespan,Died)~cohortTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,1])`, P = `r round2(summary(coxph(with(juv12,Surv(Lifespan,Died)~cohortTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,6])`). $\Delta$RTL was not related to longer-term survival (estimate `r round3(summary(coxph(with(subset(Loss,LayYear<2008),Surv(RemainingLife2+1,Died)~Loss+Agemonths)))$coefficients[1,1])`, P = `r round2(summary(coxph(with(subset(Loss,LayYear<2008),Surv(RemainingLife2+1,Died)~Loss)))$coefficients[1,5])`).

@@

temp <- dd
temp$y <- ifelse(temp$CqTelomere<15,0,1)

summary(glm(y~Ageclass+Sex+Helper,data=temp,family = 'binomial'))

ggplot(temp,aes(y = RTL,x = Ageclass))+
geom_boxplot()

### 2016-06-27 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More edits

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col='darkgrey')+
  annotate('text',x = 1,y = 2.1,label = 'A')

@@

temp <- juv_r
temp$LogAge <- log(temp$Agemonths)

#Run the model
lm2 <- lmer(RTL ~  LogAge* (Helper)+Tarsus + NonHelper + Sex + BodyMass  +yday*LogAge + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

temp[,'Helpers'] <- ifelse(temp$Helper>0,'Present', 'Absent')
temp[,'Non helpers'] <- ifelse(temp$NonHelper>0,'Present', 'Absent')
temp[,'Age (months)'] <- factor(temp$Agemonths)

Fig3B <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL)) +
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point(col = 'grey')+
  stat_smooth(method = 'lm',col = 'darkgrey')+
  annotate('text',x = 17,y = 2.1,label = 'B')

Fig3C <- ggplot(temp,
       aes(
           y = RTL,
           x=Agemonths,
       col = factor(Helper))) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm',formula = y~log(x))+
  scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')

@@

temp <- subset(dd,DeltaAge !=0)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>3])
temp <- subset(temp,BirdID %in% keep)

mins <- tapply(temp$Agemonths,temp$BirdID,min)
keep2 <- names(mins[mins <5])
temp <- subset(temp,BirdID %in% keep2)
temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

@@

Fig4B <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
geom_point()+
geom_line()+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  scale_colour_brewer(palette = 'Set1')+
  annotate('text',x = 0,y = 2,label = 'B')

>>>>

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point()+
    stat_smooth(col = 'darkgrey',lty = 3,se = F)+
  stat_smooth(method = 'lm',col='darkgrey',formula = y~log(x),se = F)
  annotate('text',x = 1,y = 2.8,label = 'A')

@@

temp <- subset(juv_r,Season == 'Major')
temp$LogAge <- log(temp$Agemonths)

#Run the model
lm2 <- lmer(CqTelomere ~  LogAge* (Helper)+Tarsus + NonHelper + Sex + BodyMass  +yday*LogAge + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

temp[,'Helpers'] <- ifelse(temp$Helper>0,'Present', 'Absent')
temp[,'Non helpers'] <- ifelse(temp$NonHelper>0,'Present', 'Absent')
temp[,'Age (months)'] <- factor(temp$Agemonths) 
temp$Age2 <- ifelse(temp$Ageclass == 'A','Adults','Juveniles')

Fig3B <- ggplot(temp,
       aes(x = Tarsus,
           y = RTL,
           col = Age2)) +
  ylab('RTL') + 
  xlab('Tarsus length (mm)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
  stat_smooth(method = 'lm')+
  annotate('text',x = 17,y = 2.1,label = 'B')

Fig3C <- ggplot(temp,
       aes(
           y = RTL,
           x=yday,
       col = (Ageclass))) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
   stat_smooth()+
  # scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  # scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')

@@

temp <- subset(dd,DeltaAge !=0)
reps <- tapply(temp$RTL,temp$BirdID,length)
keep <- names(reps[reps>3])
temp <- subset(temp,BirdID %in% keep)
 temp <- subset(temp,!duplicated(paste0(BirdID,Agemonths)))

 mins <- tapply(temp$Agemonths,temp$BirdID,min)
 keep2 <- names(mins[mins <5])
 temp <- subset(temp,BirdID %in% keep2)

@@

Fig4B <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
geom_line(col = 'darkgrey')+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  #scale_colour_brewer(palette = 'Set1')+
  annotate('text',x = 0,y = 2,label = 'B')
